\chapter{Introduction}
Information communication has become an integral part of the fabric of our society, influencing how we connect, learn, work, and interact with one another. Advancements in data transmission and standardized communications protocols have transformed the way we communicate and exchange information. They enable us to bridge geographical boundaries, maintaining relationships and forming new connections across the globe. Furthermore, they play a pivotal role in business and commerce, enabling seamless collaboration, efficient transactions, and global market access. And lastly, communication systems facilitate civic engagement, empowering individuals to voice their opinions, participate in political processes, and advocate for social change.

An important application of information communication is the data sent for control and usage of sensors, peripheral devices, and processing nodes. Communication protocols for these purposes often involve the use of short length messages and a convolutional coding scheme aided by a Cyclic Redundancy Check (CRC). This coding scheme is used in modern cell phone standards \cite{ETSI_conf} and even space communication systems \cite{Space_appl}. Furthermore, adding a tail biting condition (TB) for frame synchronization has shown to approach the RCU bound with a large number of states \cite{coskun}. 

This project aims to implement a scalable list decoder on an FPGA that can provide a maximum likelihood decoding of CRC aided tail biting convolutional codes (TBCC). We also introduce a hardware implementation of a additive white gaussian noise (AWGN) generator for accelerating end to end simulation of code performance.

